Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-15 fully-abstract-comp/technical-report.tex
changed the name of lea again to cca (change current address). Added implmentation of cca, restrict and subseg.

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\ssca}[2]{\twoinstr{\src{sca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}

@@

% Two arguments
\newcommand{\tjnz}[2]{\twoinstr{\trg{jnz}}{#1}{#2}}
\newcommand{\tisptr}[2]{\twoinstr{\trg{gettype}}{#1}{#2}}
\newcommand{\tgeta}[2]{\twoinstr{\trg{geta}}{#1}{#2}}
\newcommand{\tgetb}[2]{\twoinstr{\trg{getb}}{#1}{#2}}
\newcommand{\tgete}[2]{\twoinstr{\trg{gete}}{#1}{#2}}
\newcommand{\tgetp}[2]{\twoinstr{\trg{getp}}{#1}{#2}}
%\newcommand{\tgetloc}[2]{\twoinstr{\trg{getloc}}{#1}{#2}}
\newcommand{\tgetlin}[2]{\twoinstr{\trg{getl}}{#1}{#2}}
\newcommand{\tmove}[2]{\twoinstr{\trg{move}}{#1}{#2}}
\newcommand{\tstore}[2]{\twoinstr{\trg{store}}{#1}{#2}}
\newcommand{\tload}[2]{\twoinstr{\trg{load}}{#1}{#2}}
\newcommand{\tsca}[2]{\twoinstr{\trg{sca}}{#1}{#2}}
\newcommand{\txjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\tsetatob}[2]{\twoinstr{\trg{seta2b}}{#1}{#2}}

@@

%%% Permissions
\newcommand{\plainperm}[1]{\mathrm{#1}}
%\newcommand{\rwlx}{\plainperm{rwlx}}
\newcommand{\rwx}{\plainperm{rwx}}
\newcommand{\rx}{\plainperm{rx}}
%\newcommand{\rwlxo}{\plainperm{rwlxo}}
%\newcommand{\rwlo}{\plainperm{rwlo}}
%\newcommand{\rwl}{\plainperm{rwl}}
%\newcommand{\rwxo}{\plainperm{rwxo}}
%\newcommand{\rwo}{\plainperm{rwo}}
\newcommand{\rw}{\plainperm{rw}}
%\newcommand{\rxo}{\plainperm{rxo}}
%\newcommand{\ro}{\plainperm{ro}}
\newcommand{\readonly}{\plainperm{r}}
\newcommand{\noperm}{\plainperm{0}}
%\newcommand{\nopermo}{\plainperm{0o}}
\newcommand{\enter}{\plainperm{e}}
%\newcommand{\entero}{\plainperm{eo}}

@@

\newcommand{\encType}[1]{\plainfun{encodeType}{#1}}
\newcommand{\encPerm}[1]{\plainfun{encocePermission}{#1}}
\newcommand{\updPcAddr}[1]{\plainfun{updatePc}{#1}}
\newcommand{\updPcPerm}[1]{\plainfun{updatePcPerm}{#1}}
\newcommand{\nonExec}[1]{\plainfun{nonExecutable}{#1}}
%\newcommand{\opaquePerm}[1]{\plainfun{opaquePerm}{#1}}
\newcommand{\readAllowed}[1]{\plainfun{readAllowed}{#1}}
\newcommand{\writeAllowed}[1]{\plainfun{writeAllowed}{#1}}
%\newcommand{\writeLocalAllowed}[1]{\plainfun{writeLocalAllowed}{#1}}
%\newcommand{\nonLoc}[1]{\plainfun{nonLocal}{#1}}
\newcommand{\nonLinear}[1]{\plainfun{nonLinear}{#1}}
%\newcommand{\isLoc}[1]{\plainfun{isLocal}{#1}}
\newcommand{\isLinear}[1]{\plainfun{isLinear}{#1}}
\newcommand{\noRetStkReg}[1]{\plainfun{noRetStk_{reg}}{#1}}
\newcommand{\noRetStkMs}[1]{\plainfun{noRetStk_{ms}}{#1}}
\newcommand{\withinBounds}[1]{\plainfun{withinBounds}{#1}}
\newcommand{\nonZero}[1]{\plainfun{nonZero}{#1}}

@@

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities, local capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tsca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \\
      & & \tsplice{\trg{r}}{\trg{r}}{\trg{r}} \mid  \tsplit{\trg{r}}{\trg{r}}{\trg{r}}
\end{array}
\]

@@

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{\Phi\update{\mem.a}{w}\update{\reg.r_2}{w_2}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        (\isLinear{w} \rightarrow w_2 = 0) \tand \\
                                        (\nonLinear{w} \rightarrow w_2 = w)
                                      \end{array}
                                      \\
                                      \src{\updPcAddr{\Phi\update{\mem_\stk.a}{w}\update{\reg.r_2}{w_2}}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \src{\Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                        \src{\perm \in \writeAllowed{} \tand} \\
                                        \src{\withinBounds{\Phi(r_1)} \tand} \\
                                        \src{w = \Phi(r_2) \tand} \\
                                        \src{(\isLinear{w} \Rightarrow w_2 = 0) \tand} \\
                                        \src{(\nonLinear{w} \Rightarrow w_2 = w)}
                                      \end{array}\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}

@@

\noindent\textbf{sca}\\
\emph{Set Current Address}
\begin{align*}
  \sem{\tsca{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \dots & \dots \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

@@

\begin{align*}
  \tsem{\tsca{r_1}{r_2}} = & \dots
\end{align*}

>>>>

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\scca}[2]{\twoinstr{\src{cca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}

@@

% Two arguments
\newcommand{\tjnz}[2]{\twoinstr{\trg{jnz}}{#1}{#2}}
\newcommand{\tisptr}[2]{\twoinstr{\trg{gettype}}{#1}{#2}}
\newcommand{\tgeta}[2]{\twoinstr{\trg{geta}}{#1}{#2}}
\newcommand{\tgetb}[2]{\twoinstr{\trg{getb}}{#1}{#2}}
\newcommand{\tgete}[2]{\twoinstr{\trg{gete}}{#1}{#2}}
\newcommand{\tgetp}[2]{\twoinstr{\trg{getp}}{#1}{#2}}
%\newcommand{\tgetloc}[2]{\twoinstr{\trg{getloc}}{#1}{#2}}
\newcommand{\tgetlin}[2]{\twoinstr{\trg{getl}}{#1}{#2}}
\newcommand{\tmove}[2]{\twoinstr{\trg{move}}{#1}{#2}}
\newcommand{\tstore}[2]{\twoinstr{\trg{store}}{#1}{#2}}
\newcommand{\tload}[2]{\twoinstr{\trg{load}}{#1}{#2}}
\newcommand{\tcca}[2]{\twoinstr{\trg{cca}}{#1}{#2}}
\newcommand{\txjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\tsetatob}[2]{\twoinstr{\trg{seta2b}}{#1}{#2}}

@@

%%% Permissions
\newcommand{\plainperm}[1]{\textsc{#1}}
%\newcommand{\rwlx}{\plainperm{rwlx}}
\newcommand{\rwx}{\plainperm{rwx}}
\newcommand{\rx}{\plainperm{rx}}
%\newcommand{\rwlxo}{\plainperm{rwlxo}}
%\newcommand{\rwlo}{\plainperm{rwlo}}
%\newcommand{\rwl}{\plainperm{rwl}}
%\newcommand{\rwxo}{\plainperm{rwxo}}
%\newcommand{\rwo}{\plainperm{rwo}}
\newcommand{\rw}{\plainperm{rw}}
%\newcommand{\rxo}{\plainperm{rxo}}
%\newcommand{\ro}{\plainperm{ro}}
\newcommand{\readonly}{\plainperm{r}}
\newcommand{\noperm}{\plainperm{0}}
%\newcommand{\nopermo}{\plainperm{0o}}
\newcommand{\enter}{\plainperm{e}}
%\newcommand{\entero}{\plainperm{eo}}

@@

\newcommand{\encType}[1]{\plainfun{encodeType}{#1}}
\newcommand{\encPerm}[1]{\plainfun{encocePerm}{#1}}
\newcommand{\decPerm}[1]{\plainfun{decodePerm}{#1}}
\newcommand{\updPcAddr}[1]{\plainfun{updatePc}{#1}}
\newcommand{\updPcPerm}[1]{\plainfun{updatePcPerm}{#1}}
\newcommand{\nonExec}[1]{\plainfun{nonExecutable}{#1}}
%\newcommand{\opaquePerm}[1]{\plainfun{opaquePerm}{#1}}
\newcommand{\readAllowed}[1]{\plainfun{readAllowed}{#1}}
\newcommand{\writeAllowed}[1]{\plainfun{writeAllowed}{#1}}
%\newcommand{\writeLocalAllowed}[1]{\plainfun{writeLocalAllowed}{#1}}
%\newcommand{\nonLoc}[1]{\plainfun{nonLocal}{#1}}
\newcommand{\nonLinear}[1]{\plainfun{nonLinear}{#1}}
%\newcommand{\isLoc}[1]{\plainfun{isLocal}{#1}}
\newcommand{\isLinear}[1]{\plainfun{isLinear}{#1}}
\newcommand{\noRetStkReg}[1]{\plainfun{noRetStk_{reg}}{#1}}
\newcommand{\noRetStkMs}[1]{\plainfun{noRetStk_{ms}}{#1}}
\newcommand{\withinBounds}[1]{\plainfun{withinBounds}{#1}}
\newcommand{\nonZero}[1]{\plainfun{nonZero}{#1}}

@@

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities, local capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \\
      & & \tsplice{\trg{r}}{\trg{r}}{\trg{r}} \mid  \tsplit{\trg{r}}{\trg{r}}{\trg{r}}
\end{array}
\]

@@

We assume functions $\decPerm{}$ and $\encPerm{}$.
\lau{15-09-2017: TOOD, write more about these. Should be like in the local cap setting.}

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{\Phi\update{\mem.a}{w}\updReg{r_2}{w_2}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        (\isLinear{w} \rightarrow w_2 = 0) \tand \\
                                        (\nonLinear{w} \rightarrow w_2 = w)
                                      \end{array}
                                      \\
                                      \src{\updPcAddr{\Phi\update{\mem_\stk.a}{w}\updReg{r_2}{w_2}}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \src{\Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                        \src{\perm \in \writeAllowed{} \tand} \\
                                        \src{\withinBounds{\Phi(r_1)} \tand} \\
                                        \src{a \in \dom(\Phi.\ms_\stk) \tand} \\
                                        \src{w = \Phi(r_2) \tand} \\
                                        \src{(\isLinear{w} \Rightarrow w_2 = 0) \tand} \\
                                        \src{(\nonLinear{w} \Rightarrow w_2 = w)}
                                      \end{array}\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}

@@

\noindent\textbf{cca}\\
\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r_1}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      \perm \neq \enter \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r_1}{c}}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \src{\text{either $n = r_2$ or $n = \Phi(r_2)$ and in either case $n \in \ints$ and}} \\
                                      \src{\Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                      \src{\perm \neq \enter \tand} \\
                                      \src{c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}}
                                    \end{array}
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{r_3}} = &
                                      \begin{cases}
                                        \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \isLinear{\Phi(r_2)} \Rightarrow w_2 = 0 \tand \\
                                          \nonLinear{\Phi(r_2)} \Rightarrow w_2 = \Phi(r_2) \tand \\
                                        \end{array}
                                        \\
                                        \src{\Phi\updReg{r_2}{0}\updReg{r_1}{c}} &
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \src{\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                          \src{\text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and}} \\
                                          \src{\decPerm{n} \sqsubseteq \perm \tand} \\
                                          \src{c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}}
                                        \end{array}
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

\noindent\textbf{subseg}\\
\begin{align*}
  \sem{\tsubseg{r_1}{r_2}{r_3}{r_4}}(\Phi) = &
                                               \begin{cases}
                                                 \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \text{for $i \in \{3, 4\}$ } \\
                                                   \quad \text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}\\
                                                   \quad \text{and in either case $n_i \in \ints$ and} \\
                                                   \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \baddr \leq n_3 \tand 
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand \\
                                                   (n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand\\
                                                   \perm \neq \enter \tand\\
                                                   c = ((\perm,\lin),n_1,\eaddr',\aaddr)\\
                                                   \isLinear{\Phi(r_2)} \Rightarrow w_2 = 0 \tand \\
                                                   \nonLinear{\Phi(r_2)} \Rightarrow w_2 = \Phi(r_2) \tand
                                                 \end{array}
\\
                                                 \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \text{for $i \in \{3, 4\}$ } \\
                                                   \quad \text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}\\
                                                   \quad \text{and in either case $n_i \in \ints$ and} \\
                                                   \Phi(r_2) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr} \tand \\
                                                   \baddr \leq n_3 \tand 
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand \\
                                                   (n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand\\
                                                   \perm \neq \enter \tand\\
                                                   c = \seal{\lin,n_1,\eaddr'}\\
                                                   \isLinear{\Phi(r_2)} \Rightarrow w_2 = 0 \tand \\
                                                   \nonLinear{\Phi(r_2)} \Rightarrow w_2 = \Phi(r_2) \tand
                                                 \end{array}
\\
                                                 \src{\Phi\updReg{r_2}{0}\updReg{r_1}{c}} &
                                                 \arraycolsep=0pt
                                                 \begin{array}[t]{l}
                                                   \src{\text{for $i \in \{3, 4\}$ }} \\
                                                   \quad \src{\text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}}\\
                                                   \quad \src{\text{and in either case $n_i \in \ints$ and}} \\
                                                   \src{\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                                   \src{\baddr \leq n_3 \tand }
                                                   \src{(n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand }\\
                                                   \src{(n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand}\\
                                                   \src{\perm \neq \enter \tand}\\
                                                   \src{c = \stkptr{\perm,n_1,\eaddr',\aaddr}}\\
                                                 \end{array}\\
                                                 \failed & \totherwise 
                                               \end{cases}
\end{align*}

@@

\begin{align*}
  \tsem{\tcca{r_1}{r_2}} = & \dots
\end{align*}
